\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-16 paper/paper.tex
background pass
Terminology

Our deployment model is identical to that of TapDance: we only require a passive
tap at the deploying ISP, and the ability to inject (spoofed) traffic from dark
decoy sites.
Furthermore, we assume
asymmetric routing (i.e. that the tap can sometimes only see packets from but not to the
client).
However, we assume a stronger threat model for the adversary than
TapDance, as our design resists active attacks.

@@

We assume that the censor can know what network the dark decoy station(s) are
deployed in and the prefixes dark decoys are selected from, but that blocking those
networks outright brings a collateral
damage the censor is unwilling to suffer. Instead, the censor aims to identify
the addresses that are dark decoys, and block only those.

We assume the censor can use the client to register and access its own dark
decoys, but that these will not reveal the dark decoys of other users. The
censor can also actively probe addresses that it sees users accessing, but can
not enumerate the entire dark decoy prefix (e.g. a /32 IPv6 prefix contains
$2^{96} addresses$).

Finally, we assume the censor can replay or preplay any connections that it
suspects involve dark decoys (or their registration) in an attempt to confirm.
However, the censor wishes to avoid disrupting any connections before it
knows for certain they are dark decoy ones, lest they disrupt legitimate
connections. This means that injecting false data or corrupting TLS sessions is
outside the scope of the censor, but that the censor can send non-disruptive
probes (such as stale TCP acknowledgements or other packets that would normally
be ignored). We emphasize that TapDance is observable by censors that can send
TCP packets in suspected connections, but that our protocol is robust against
this class of censor.

@@

\scheme involve three main steps. First, clients \textbf{register} with the
ISP station,
and agree on the dark decoy IP address that will be used. Next, the client
connects to the agreed upon address, which is terminated by an
\textbf{application} running on the station. Finally, the client \textbf{proves}
to the application that it was the same client that registered (and not a censor
attempting to probe), and is able to use the application as a proxy.

@@

Inside the message, the client communicates a random \textbf{seed}, and other
configuration-specific information, such as flags to signify version, feature
support, and a set of IPv6 network prefixes that the client knows can be used
for dark decoys (previously distributed publicly).
The client and server hash the seed to determine which specific
IPv6 address from the set of prefixes will be used and registered as a dark
decoy. It may seem intuitive to instead have the client
send the specific IP address to register, but allowing the client arbitrary
choice also allows the censor to register suspected dark decoys and block them if
they pick up. 
By using a hash of a seed, the censor would have to pre-image the hash to
obtain a seed it could use to register for a desired IP address.
It also gives a
secret (the seed) that only the client and station know, even after the client
connects to the dark decoy address.

Once the dark decoy IP address has been selected, the station watches for
packets destined to that address, and forwards them onto the dark decoy
\textbf{application}. The station can also optionally ignore packets not from
the source IP address of the registering client, so that to a probing censor
from a different IP address,
the dark decoy appears to be firewalled off from all but the client. We note
this is not a robust solution: censors have previously been observed taking over
IP addresses of clients~\cite{ensafi-tor}. We instead address active probing in
the application.

\subsubsection{IPv6 vs IPv4 dark decoys}

Dark decoy IP addresses must be derived from network blocks that are routed (so they pass
the ISP station) and contain other legitimate hosts (so that censors cannot
block the entire network without collateral damage).
Because of the large number of IPv6 addresses, even
relatively small network prefixes have astronomical numbers of addresses: a
single /32 prefix has $2^{96}$ possible addresses. Therefore, client-chosen
seeds have negligible probability of corresponding to addresses that are already
being used by legitimate hosts. This allows us to select dark decoy addresses
from network prefixes that contain
legitimate hosts---crucial to discouraging the censor from blocking them
outright---without worry that registrations could interfere with legitimate
services.

In addition, the use of IPv6 prevents censors from exhaustively probing
potential dark decoy network prefixes ahead of time to learn the full set of
legitimate sites in the network.

\paragraph{IPv4}
While \scheme composes well with IPv6, we can also support IPv4,
at the cost of being vulnerable to active probing by the censor.
We emphasize that TapDance is already
vulnerable to active probing attacks~\cite{tapdance14} that \scheme defends
against when using IPv6. However, in IPv4, there are substantially fewer
addresses, allowing censors to easily enumerate network prefixes that pass by
the ISP station and measure legitimate sites. Furthermore, the small address
space makes it much easier to pre-image the hash used to derive IP addresses
from the seed. Registering a specific IPv4 address in an IPv4 /16 subnet will
take only an expected $2^{16}$ hashes for the censor to achieve. This would let
attackers register legitimate hosts as dark decoys, potentially disrupting
legitimate service. If the station refused to pick up for addresses that
correspond to legitimate hosts (measured by scanning during registration), then
censors could use this as an oracle for distinguishing legitimate sites from
dark decoys. Still, IPv4 \scheme offers many performance, flexibility, and
simplicity benefits over TapDance, though they are both vulnerable to active
probing attacks.

@@

Once the client has registered, packets sent to the dark decoy IP address are
passed to the \textbf{application} running on the station. The application has
two main jobs: first, it must look like an innocuous legitimate service to the
censor, and second must allow the client to use it as a proxy.

@@

TLS is a natural protocol for dark decoy applications, because it is ubiquitous on
the Internet (making it difficult for censors to block), while also providing
strong cryptographic protection against passive and active network adversaries.
However, there are several challenges to make it robust against censors that
wish to block a particular service.

@@

Selecting which sites to masquerade as must be done carefully to avoid censors
being able to detect obvious choices. For example, if a small university network
has a dark decoy in their network that appears to be \texttt{apple.com}, it
would be easy for a censor to block as a likely non-legitimate host. Likewise,
if a dark decoy at an IP address pretends to be a domain (\texttt{example.com}) that
globally resolves to a single different IP address, the censor could also
identify and block the dark decoy.

\paragraph{Nearby sites.}
One strategy for selecting mask sites to mimic is to pick websites that are
legitimately hosted in or near the network of the dark decoy addresses. This
effectively creates copies of legitimate sites, with the censor unable to
determine which copies are real and which are the dark decoys. However, as
mentioned, other signals such as DNS may reveal the true mask site.

\paragraph{Popular sites.}
An alternative strategy is to use popular sites, such as those from the Alexa
top site~\cite{alexa-top500} list. As mentioned previously, it may be wise to avoid
sites that are obviously not hosted in the dark decoy address range, such as
large companies that run their own datacenters and own their own ASN.
The list could also be filtered to domains that resolve to different IP
addresses from different vantage points, making it harder for a censor to know
if a dark decoy corresponds to a domain's IP.

\paragraph{Passive observation.}
The ISP tap could also collect sites by passively observing DNS requests, TLS
SNI, or certificates that pass by. This would allow for building a realistic set
of sites that are plausibly in the vicinity of the dark decoy addresses
that pass by the tap. It also has the added bonus of being able to discover
IPv6 addresses that could be used as decoys (for registration), where active
scanning would be infeasible.

In practice, clients can often try multiple dark decoys/mask sites over
several attempts, as blocking the client outright may negatively impact other
unrelated users behind the same network (e.g. in the case of NAT). Thus, even a
censor that can block most (but not all) mask site only delays access, and
doesn't prevent it outright.

@@

TLS~1.3~\cite{tls13} offers several features that may greatly simplify dark
decoy application design. For instance, TLS~1.3 handshakes include encrypted
certificates, potentially obviating the need to impersonate mask sites.
Unfortunately, TLS~1.3 currently still sends the SNI in the (plaintext) Client
Hello, meaning we would still have to choose a realistic domain to fool a
censor.

However, there are proposals to encrypt the SNI in the Client Hello~\cite{esni},
though none have been implemented or deployed as of early 2019. Nonetheless,
if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for dark
decoy applications by allowing the domain to remain hidden from the censor.
While the censor could still try to actively probe with guesses for the SNI,
servers could respond with generic ``Unknown SNI'' errors. If such responses
were common for incorrect SNI, the censor's efforts to identify dark decoys
would be frustrated.

@@

Dark Decoys could also pretend to be clients instead of servers. This may
potentially give censors less to block on, as actively probing clients is common
to return few or no open ports. Nonetheless, a censor may be hesitant to block
client-to-client communication, as it could block peer-to-peer applications as
well as many video conferencing protocols. WebRTC is a
natural choice for a client-to-client protocol in censorship circumvention,
and is used in existing censorship circumvention schemes like
Snowflake~\cite{snowflake}. Dark decoy applications could also use WebRTC as the
application protocol, convincing the censor that two clients are communicating.

@@

We implemented the Dark Decoy protocol and tested it in a 10~Gbps ISP testbed
with real traffic. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
consume the 10~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
detector processes all packets and watches for new registrations. It also
forwards all packets sent to a (registered) dark decoy's address to the local
\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
allowing the application to accept and respond to connections using the native
operating system's interface. Figure~\ref{fig:implementation} shows the overall
architecture of our implementation, which we describe next.
% Along with the client?

@@

We used PF\_RING to load balance the 10~Gbps link over 4~CPU cores. PF\_RING
supports balancing across cores based on flow (5-tuple) or source and
destination IPs. However, both of these options present challenges for our Dark
Decoy detector. One issue is that registrations could be processed on a
different core than the packets sent to that specific dark decoy address. For
instance, a client could have its registration handled by Core 1, while its
packets to the dark decoy address end up on Core 3, which doesn't know about the
original registration.

To address this, we used Redis~\cite{redis} to allow each process to announce
(publish) newly registered decoys to the other cores so they can
add them to their local list of registered dark decoy addresses.
However, this introduces two new problems. First, a core might add a
registration \emph{after} it has already received and processed packets destined
for the specified dark decoy. This typically isn't a problem when running on a
single core, as packets are processed sequentially. Second, each core may
timeout each dark decoy at different times, potentially leading to differing
behavior that is visible to a censor. For instance, if we used the
source/destination IPs to load balance, a censor's packets to a dark decoy could
be processed by a different core than the client. If the censor waits for the
known timeout before sending a probe, its core may have timed out that dark
decoy, while the client's core has refreshed the timeout of the dark decoy due
to active use.

To address the first issue, we force the client to delay sending its connection
to the dark decoy until a short time after registration. In practice, we force
the client to wait until the registration decoy responds before starting a
connection with the registered dark decoy.

To address the second issue, we implemented a new load-balancing algorithm in
PF\_RING to select the core based solely on the destination IP address of the
packet. This still means we must use Redis to tell all of the cores of new
registrations, but that only one core will be responsible for processing all of
the packets sent to a given dark decoy, regardless of who or when it is sent.

@@

The application accepts connections to dark decoy addresses forwarded by the
detector and rewritten to the local address using \texttt{iptables}.
The application also receives out-of-band information about registrations from the
detector via a ZMQ~\cite{zmq} connection, which informs the application of the
registering client's IP address, the secret seed, and other configuration
information passed by the client.

@@

If the decryption is successful, the application switches to forwarding
(decrypted) data back and forth with a client-specified endpoint, such as a
SOCKS proxy, which can multiplex multiple client connections over the single
connection to the dark decoy.

@@

After registering, the client connects to the derived dark decoy address, and
switches secrets after the handshake. At this point, a local application (e.g.
SOCKS client) can connect to the client, and it will transparently be connected to
the remote end via the encrypted dark decoy connection.

@@

Implementation of the protocol includes 3 components:
dark decoy detector, proxy application, and client.
Dark decoy detector will parse the traffic, searching for registrations in
tagged messages. After detector observes a registration, and negotiates with client
a dark decoy IP,
all packets, that are sent to that dark decoy IP,
will be forwarded into a proxy application.

@@

Each Dark Decoy connection has 2 phases: registration, and usage of a dark decoy.
Registration starts with a handshake that is similar to a TapDance handshake,
but initial HTTP request is complete.
This allows a reachable site to provide a genuine response
to a HTTP GET request of its index page.
Since station does not need to produce a response,
which significantly reduces complexity of a detector,
that does not need to decrypt and inject packets into a TLS connection between
client and a reachable site, as opposed to original TapDance.

@@

Client will sleep a short randomized period of time before attempting to establish connection to dark decoy.
This is done for 2 reasons: to break potentially observable interflow dependency with a dark decoy connection being established right after a first application layer data packet sent to decoy,
and to give station time.
TODO: why does it need time?

\subsection{Application phase}
Client and station will use HKDF to derive 16 random bytes and use them to
agree on a dark decoy IP address, by applying a simple selection algorithm.
Algorithm is as follows: first, flatten a list of pre-shared avaliable IP
addresses in various subnets into a single indexed list, then make a 128-bit
integer out of 16 random bytes and divide it by the length
of the flattened list, and use the remainder of this division as an index
of the list to pick an IP address.

@@

Note that dark decoy detector and proxy application are only loosely coupled with each other,
making it simple to replace one of them.
We plan to take advantage of encrypted SNI, when it gets widely adopted,
and replace our current proxy implementation with one that uses encrypted SNI
and achieve improved unobservability properties, described in section~\ref{esni}.

@@

\subsection{Attacks and Defenses}
% 1 page

There are many attacks a censor might attempt to either prevent dark decoys from
being registered or used.

\paragraph{Blocking registration}
To make registration more difficult, censors could block TLS connections to all of the
limited decoys available in a deployment. Using TapDance's current deployment,
this would involve blocking over 1500 sites. We note that such an attack would
completely disable all existing Refraction Networking schemes, as none work
without being able to access legitimate decoys past the station. In dark decoys,
this would only block new registrations, and would not impact users that
previously registered. Furthermore, registrations could also occur over email,
or over lower-bandwidth covert channels, such as port (or even IP) knocking past
the station, that would be more difficult for the censor to block.
%Cirripede previously used a registration protocol that sent covert information via initial
%sequence numbers in arbitrary TCP connections, though we note this solution
%generally requires clients to have root access to their device to control the
%initial sequence numbers. Since most mobile users do not have such control, we
%suggest other methods be used instead.

\paragraph{Scanning masked sites}
The censor could also attempt to fingerprint the masked site and compare it to a
suspected dark decoy application. For instance, if a dark decoy IP responds as
pretending to be \texttt{example.com}, the censor could scan or probe real instances
of \texttt{example.com} on different ports and see how it responds. Then, the
censor can probe the dark decoy IP, and see if it responds similarly (e.g. with
the same set of open ports and payloads for certain kinds of probes). To defend
against this, we forward \emph{all} traffic destined to the dark decoy to the
masked site, including ports that are not relevant to the proxy application
(e.g. non 443). This ensures that above the TCP layer, we appear to be the mask
site. However, there may be differences in TCP/IP implementations, for instance,
how IP IDs are incremented, or how TCP timestamps are incremented (or supported
at all) that may be different from the mask site. To combat this, we can filter
mask sites by those that have identical TCP/IP stacks to ours, as we use a
common Linux implementation. We also note that this attack only applies when we
use the mask site as an application, and that Dark Decoys can support other
applications (e.g. obfsproxy, WebRTC, etc) that do not have this issue.

@@

Dark Decoy applications that mimic specific websites (e.g., mask sites) are likewise susceptible to WF. To date, however, censors have not been observed using WF and similar techniques, possibly due to the significant uncertainty resulting from even the best algorithms: even a small false
positive rate means blocking mostly legitimate connections (due to the base rate
of normal traffic), and false negatives could allow clients to retry until they
gain access.

More importantly, Dark Decoy applications offer great flexibility in deploying traffic analysis defenses; for example, traffic shaping strategies such as implemented in Slitheen~\cite{slitheen16} could be easily employed in Dark Decoys. Furthermore,
Dark Decoy applications are not limited to mimicking websites, and can support
any (or even a combination of) protocols. Finally, if encrypted SNI can be used (\cref{esni}), the censor would not be able to build up a traffic profile of a legitimate site since its identity would be encrypted.

\paragraph{ICMP}
Censors can use ping or traceroute utilities (via ICMP) to probe potential dark
decoys. Because there is (usually) no host at the dark decoy address, these
probes will timeout and produce no response. They might also produce
``Destination Unreachable'' responses from routers depending on how they are
configured. We performed a scan of 10~million IPv6 addresses in a routable /32
prefix to see if it is common to respond with such tell-tale ICMP messages for
unused messages. We found only 0.016\% of addresses responded with any ICMP
messages (a combination of ``Time Exceeded'' and ``Destination Unreachable'').

Many legitimate hosts and routers do not respond to or forward ICMP packets, and
it is common for firewalls to block traceroutes from penetrating inside
networks. Thus, simply ignoring ICMP messages (or low TTL packets that might be
used by traceroute) may be a viable strategy. % We should evaluate this claim...
Alternatively, we could spoof responses to convince an adversary that a dark
decoy is part of a particular network. However, this strategy requires careful
consideration of what network makes sense for a mask site to be in. Also, the
censor may try to probe for addresses around the dark decoy (but still likely to
be in the same network), which must also be responded to.

@@

\paragraph{Address entropy}
Addresses in IPv6 are commonly shortened, as many of the 128-bits in the address are set to 0.
For instance, google.com has the address
\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
\texttt{2607:f8b0:400f:806::2004}). Only 24 bits are set to 1 in this address,
giving censors a possible feature to filter on: addresses that have too much
entropy (or even simply bits set) could be suspicious as dark decoys. To demonstrate and quantify
this problem, we measured 30 minutes of IPv6 traffic to our ISP's /32 network prefix.
Figure~\ref{fig:ipbits} shows a histogram of bits set in the addresses we observed, which are
notably skewed to less than expected if addresses were randomly generated. However, there
are still a significant number of networks that appear to have random-looking addresses,
making it difficult for censors to block these addresses outright. For a specific deployment,
operators should be careful to observe the distribution of addresses in the subnets they use,
and possibly limit to randomizing ``realistic'' bits (e.g. the middle and/or last 32 bits).

@@

\paragraph{Client-side applications}
On the application side, \scheme provides an interesting opportunity to explore
\emph{client mimicking} dark decoys. Rather than pretend to be a server (e.g.
mask site), our application could connect back to a client after registration
from the dark decoy address. Protocols like WebRTC mentioned in
Section~\ref{sec:webrtc} or other peer-to-peer protocols such as BitTorrent,
Skype, or Bitcoin.

>>>>

Our deployment model is identical to that of TapDance: we only require a passive
tap at the deploying ISP, and the ability to inject (spoofed) traffic from phantom
hosts.
Furthermore, we assume
asymmetric routing (i.e. that the tap can sometimes only see packets from but not to the
client).
However, we assume a stronger threat model for the adversary than
TapDance, as our design resists active attacks.

@@

We assume that the censor can know what network the \scheme station(s) are
deployed in and the prefixes phantom hosts are selected from, but that blocking those
networks outright brings a collateral
damage the censor is unwilling to suffer. Instead, the censor aims to identify
the addresses that are phantom hosts, and block only those.

We assume the censor can use the client to register and access its own phantom
hosts, but that these will not reveal the phantom hosts of other users. The
censor can also actively probe addresses that it sees users accessing, but can
not enumerate the entire ISP prefix (e.g. a /32 IPv6 prefix contains
$2^{96} addresses$).

Finally, we assume the censor can replay or preplay any connections that it
suspects involve phantom hosts (or their registration) in an attempt to confirm.
However, the censor wishes to avoid disrupting any connections before it
knows for certain they are from \scheme clients, lest they disrupt legitimate
connections. This means that injecting false data or corrupting TLS sessions is
outside the scope of the censor, but that the censor can send non-disruptive
probes (such as stale TCP acknowledgements or other packets that would normally
be ignored). We emphasize that TapDance is observable by censors that can send
TCP packets in suspected connections, but that our protocol is robust against
this class of censor.

@@

\scheme involve three main steps. First, clients \textbf{register} with the
ISP station,
and agree on the phantom host IP address that will be used. Next, the client
connects to the agreed upon address, which is terminated by an
\textbf{application} running on the station. Finally, the client \textbf{proves}
to the application that it was the same client that registered (and not a censor
attempting to probe), and is able to use the application as a proxy.

@@

Inside the message, the client communicates a random \textbf{seed}, and other
configuration-specific information, such as flags to signify version, feature
support, and a set of IPv6 network prefixes that the client knows can be used
for phantom hosts (previously distributed publicly).
The client and server hash the seed to determine which specific
IPv6 address from the set of prefixes will be used and registered as a phantom host. It may seem intuitive to instead have the client
send the specific IP address to register, but allowing the client arbitrary
choice also allows the censor to register suspected phantom hosts and block them if
they pick up. 
By using a hash of a seed, the censor would have to pre-image the hash to
obtain a seed it could use to register for a desired IP address.
It also gives a
secret (the seed) that only the client and station know, even after the client
connects to the phantom host address.

Once the phantom host IP address has been selected, the station watches for
packets destined to that address, and forwards them onto the phantom host
\textbf{application}. The station can also optionally ignore packets not from
the source IP address of the registering client, so that to a probing censor
from a different IP address,
the phantom host appears to be firewalled off from all but the client. We note
this is not a robust solution: censors have previously been observed taking over
IP addresses of clients~\cite{ensafi-tor}. We instead address active probing in
the application.

\subsubsection{IPv6 vs IPv4 phantom hosts}

Phantom host IP addresses must be derived from network blocks that are routed (so they pass
the ISP station) and contain other legitimate hosts (so that censors cannot
block the entire network without collateral damage).
Because of the large number of IPv6 addresses, even
relatively small network prefixes have astronomical numbers of addresses: a
single /32 prefix has $2^{96}$ possible addresses. Therefore, client-chosen
seeds have negligible probability of corresponding to addresses that are already
being used by legitimate hosts. This allows us to select phantom host addresses
from network prefixes that contain
legitimate hosts---crucial to discouraging the censor from blocking them
outright---without worry that registrations could interfere with legitimate
services.

In addition, the use of IPv6 prevents censors from exhaustively probing
potential phantom host network prefixes ahead of time to learn the full set of
legitimate sites in the network.

\paragraph{IPv4}
While \scheme composes well with IPv6, we can also support IPv4,
at the cost of being vulnerable to active probing by the censor.
We emphasize that TapDance is already
vulnerable to active probing attacks~\cite{tapdance14} that \scheme defends
against when using IPv6. However, in IPv4, there are substantially fewer
addresses, allowing censors to easily enumerate network prefixes that pass by
the ISP station and measure legitimate sites. Furthermore, the small address
space makes it much easier to pre-image the hash used to derive IP addresses
from the seed. Registering a specific IPv4 address in an IPv4 /16 subnet will
take only an expected $2^{16}$ hashes for the censor to achieve. This would let
attackers register legitimate hosts as phantom hosts, potentially disrupting
legitimate service. If the station refused to pick up for addresses that
correspond to legitimate hosts (measured by scanning during registration), then
censors could use this as an oracle for distinguishing legitimate sites from
phantom hosts. Still, IPv4 \scheme offers many performance, flexibility, and
simplicity benefits over TapDance, though they are both vulnerable to active
probing attacks.

@@

Once the client has registered, packets sent to the phantom host IP address are
passed to the \textbf{application} running on the station. The application has
two main jobs: first, it must look like an innocuous legitimate service to the
censor, and second must allow the client to use it as a proxy.

@@

TLS is a natural protocol for \scheme applications, because it is ubiquitous on
the Internet (making it difficult for censors to block), while also providing
strong cryptographic protection against passive and active network adversaries.
However, there are several challenges to make it robust against censors that
wish to block a particular service.

@@

Selecting which sites to masquerade as must be done carefully to avoid censors
being able to detect obvious choices. For example, if a small university network
has a phantom host in their network that appears to be \texttt{apple.com}, it
would be easy for a censor to block as a likely non-legitimate host. Likewise,
if a phantom host at an IP address pretends to be a domain (\texttt{example.com}) that
globally resolves to a single different IP address, the censor could also
identify and block the phantom host.

\paragraph{Nearby sites.}
One strategy for selecting mask sites to mimic is to pick websites that are
legitimately hosted in or near the network of the phantom host addresses. This
effectively creates copies of legitimate sites, with the censor unable to
determine which copies are real and which are the phantom hosts. However, as
mentioned, other signals such as DNS may reveal the true mask site.

\paragraph{Popular sites.}
An alternative strategy is to use popular sites, such as those from the Alexa
top site~\cite{alexa-top500} list. As mentioned previously, it may be wise to avoid
sites that are obviously not hosted in the phantom host address range, such as
large companies that run their own datacenters and own their own ASN.
The list could also be filtered to domains that resolve to different IP
addresses from different vantage points, making it harder for a censor to know
if a phantom host corresponds to a domain's IP.

\paragraph{Passive observation.}
The ISP tap could also collect sites by passively observing DNS requests, TLS
SNI, or certificates that pass by. This would allow for building a realistic set
of sites that are plausibly in the vicinity of the phantom host addresses
that pass by the tap. It also has the added bonus of being able to discover
IPv6 addresses that could be used as decoys (for registration), where active
scanning would be infeasible.

In practice, clients can often try phantom hosts/mask sites over
several attempts, as blocking the client outright may negatively impact other
unrelated users behind the same network (e.g. in the case of NAT). Thus, even a
censor that can block most (but not all) mask site only delays access, and
doesn't prevent it outright.

@@

TLS~1.3~\cite{tls13} offers several features that may greatly simplify 
\scheme application design. For instance, TLS~1.3 handshakes include encrypted
certificates, potentially obviating the need to impersonate mask sites.
Unfortunately, TLS~1.3 currently still sends the SNI in the (plaintext) Client
Hello, meaning we would still have to choose a realistic domain to fool a
censor.

However, there are proposals to encrypt the SNI in the Client Hello~\cite{esni},
though none have been implemented or deployed as of early 2019. Nonetheless,
if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
\scheme applications by allowing the domain to remain hidden from the censor.
While the censor could still try to actively probe with guesses for the SNI,
servers could respond with generic ``Unknown SNI'' errors. If such responses
were common for incorrect SNI, the censor's efforts to identify phantom hosts
would be frustrated.

@@

Phantom hosts could also pretend to be clients instead of servers. This may
potentially give censors less to block on, as actively probing clients is common
to return few or no open ports. Nonetheless, a censor may be hesitant to block
client-to-client communication, as it could block peer-to-peer applications as
well as many video conferencing protocols. WebRTC is a
natural choice for a client-to-client protocol in censorship circumvention,
and is used in existing censorship circumvention schemes like
Snowflake~\cite{snowflake}. \scheme could also use WebRTC as the
application protocol, convincing the censor that two clients are communicating.

@@

We implemented the \scheme protocol and tested it in a 10~Gbps ISP testbed
with real traffic. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
consume the 10~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
detector processes all packets and watches for new registrations. It also
forwards all packets sent to a (registered) phantom host address to the local
\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
allowing the application to accept and respond to connections using the native
operating system's interface. Figure~\ref{fig:implementation} shows the overall
architecture of our implementation, which we describe next.
% Along with the client?

@@

We used PF\_RING to load balance the 10~Gbps link over 4~CPU cores. PF\_RING
supports balancing across cores based on flow (5-tuple) or source and
destination IPs. However, both of these options present challenges for our 
implementation. One issue is that registrations could be processed on a
different core than the packets sent to that specific phantom host address. For
instance, a client could have its registration handled by Core 1, while its
packets to the phantom host address end up on Core 3, which doesn't know about the
original registration.

To address this, we used Redis~\cite{redis} to allow each process to announce
(publish) newly registered decoys to the other cores so they can
add them to their local list of registered phantom host addresses.
However, this introduces two new problems. First, a core might add a
registration \emph{after} it has already received and processed packets destined
for the specified phantom host. This typically isn't a problem when running on a
single core, as packets are processed sequentially. Second, each core may
timeout each phantom host at different times, potentially leading to differing
behavior that is visible to a censor. For instance, if we used the
source/destination IPs to load balance, a censor's packets to a phantom host could
be processed by a different core than the client. If the censor waits for the
known timeout before sending a probe, its core may have timed out that phantom host, while the client's core has refreshed the timeout of the phantom host due
to active use.

To address the first issue, we force the client to delay sending its connection
to the phantom host until a short time after registration. In practice, we force
the client to wait until the registration decoy responds before starting a
connection with the registered phantom host.

To address the second issue, we implemented a new load-balancing algorithm in
PF\_RING to select the core based solely on the destination IP address of the
packet. This still means we must use Redis to tell all of the cores of new
registrations, but that only one core will be responsible for processing all of
the packets sent to a given phantom host, regardless of who or when it is sent.

@@

The application accepts connections to phantom host addresses forwarded by the
detector and rewritten to the local address using \texttt{iptables}.
The application also receives out-of-band information about registrations from the
detector via a ZMQ~\cite{zmq} connection, which informs the application of the
registering client's IP address, the secret seed, and other configuration
information passed by the client.

@@

If the decryption is successful, the application switches to forwarding
(decrypted) data back and forth with a client-specified endpoint, such as a
SOCKS proxy, which can multiplex multiple client connections over the single
connection to the phantom host.

@@

After registering, the client connects to the derived phantom host address, and
switches secrets after the handshake. At this point, a local application (e.g.
SOCKS client) can connect to the client, and it will transparently be connected to
the remote end via the encrypted phantom host connection.

@@

Implementation of the protocol includes 3 components:
detector, proxy application, and client.
Detector will parse the traffic, searching for registrations in
tagged messages. After detector observes a registration, and negotiates with client
a phantom host IP,
all packets, that are sent to that phantom host IP,
will be forwarded into a proxy application.

@@

Each \scheme connection has 2 phases: registration, and usage of a phantom host.
Registration starts with a handshake that is similar to a TapDance handshake,
but initial HTTP request is complete.
This allows a reachable site to provide a genuine response
to a HTTP GET request of its index page.
Since station does not need to produce a response,
which significantly reduces complexity of a detector,
that does not need to decrypt and inject packets into a TLS connection between
client and a reachable site, as opposed to original TapDance.

@@

Client will sleep a short randomized period of time before attempting to establish connection to phantom host.
This is done for 2 reasons: to break potentially observable interflow dependency with a phantom host connection being established right after a first application layer data packet sent to decoy,
and to give station time.
TODO: why does it need time?

\subsection{Application phase}
Client and station will use HKDF to derive 16 random bytes and use them to
agree on a phantom host IP address, by applying a simple selection algorithm.
Algorithm is as follows: first, flatten a list of pre-shared avaliable IP
addresses in various subnets into a single indexed list, then make a 128-bit
integer out of 16 random bytes and divide it by the length
of the flattened list, and use the remainder of this division as an index
of the list to pick an IP address.

@@

Note that the detector and proxy application are only loosely coupled with each other,
making it simple to replace one of them.
We plan to take advantage of encrypted SNI, when it gets widely adopted,
and replace our current proxy implementation with one that uses encrypted SNI
and achieve improved unobservability properties, described in section~\ref{esni}.

@@

\subsection{Attacks and Defenses}
% 1 page
\label{sec:attacks}

There are many attacks a censor might attempt to either prevent phantom hosts from
being registered or used.

\paragraph{Blocking registration}
To make registration more difficult, censors could block TLS connections to all of the
limited decoys available in a deployment. Using TapDance's current deployment,
this would involve blocking over 1500 sites. We note that such an attack would
completely disable all existing Refraction Networking schemes, as none work
without being able to access legitimate decoys past the station. In \scheme,
this would only block new registrations, and would not impact users that
previously registered. Furthermore, registrations could also occur over email,
or over lower-bandwidth covert channels, such as port (or even IP) knocking past
the station, that would be more difficult for the censor to block.
%Cirripede previously used a registration protocol that sent covert information via initial
%sequence numbers in arbitrary TCP connections, though we note this solution
%generally requires clients to have root access to their device to control the
%initial sequence numbers. Since most mobile users do not have such control, we
%suggest other methods be used instead.

\paragraph{Scanning masked sites}
The censor could also attempt to fingerprint the masked site and compare it to a
suspected \scheme application. For instance, if a phantom host IP responds as
pretending to be \texttt{example.com}, the censor could scan or probe real instances
of \texttt{example.com} on different ports and see how it responds. Then, the
censor can probe the phantom host IP, and see if it responds similarly (e.g. with
the same set of open ports and payloads for certain kinds of probes). To defend
against this, we forward \emph{all} traffic destined to the phantom host to the
masked site, including ports that are not relevant to the proxy application
(e.g. non 443). This ensures that above the TCP layer, we appear to be the mask
site. However, there may be differences in TCP/IP implementations, for instance,
how IP IDs are incremented, or how TCP timestamps are incremented (or supported
at all) that may be different from the mask site. To combat this, we can filter
mask sites by those that have identical TCP/IP stacks to ours, as we use a
common Linux implementation. We also note that this attack only applies when we
use the mask site as an application, and that \scheme can support other
applications (e.g. obfsproxy, WebRTC, etc) that do not have this issue.

@@

\scheme applications that mimic specific websites (e.g., mask sites) are likewise susceptible to WF. To date, however, censors have not been observed using WF and similar techniques, possibly due to the significant uncertainty resulting from even the best algorithms: even a small false
positive rate means blocking mostly legitimate connections (due to the base rate
of normal traffic), and false negatives could allow clients to retry until they
gain access.

More importantly, \scheme applications offer great flexibility in deploying traffic analysis defenses; for example, traffic shaping strategies such as implemented in Slitheen~\cite{slitheen16} could be easily employed in \scheme. Furthermore,
\scheme applications are not limited to mimicking websites, and can support
any (or even a combination of) protocols. Finally, if encrypted SNI can be used (\cref{esni}), the censor would not be able to build up a traffic profile of a legitimate site since its identity would be encrypted.

\paragraph{ICMP}
Censors can use ping or traceroute utilities (via ICMP) to probe potential phantom
hosts. Because there is (usually) no host at the phantom host address, these
probes will timeout and produce no response. They might also produce
``Destination Unreachable'' responses from routers depending on how they are
configured. We performed a scan of 10~million IPv6 addresses in a routable /32
prefix to see if it is common to respond with such tell-tale ICMP messages for
unused messages. We found only 0.016\% of addresses responded with any ICMP
messages (a combination of ``Time Exceeded'' and ``Destination Unreachable'').

Many legitimate hosts and routers do not respond to or forward ICMP packets, and
it is common for firewalls to block traceroutes from penetrating inside
networks. Thus, simply ignoring ICMP messages (or low TTL packets that might be
used by traceroute) may be a viable strategy. % We should evaluate this claim...
Alternatively, we could spoof responses to convince an adversary that a 
phantom host is part of a particular network. However, this strategy requires careful
consideration of what network makes sense for a mask site to be in. Also, the
censor may try to probe for addresses around the phantom host (but still likely to
be in the same network), which must also be responded to.

@@

\paragraph{Address entropy}
Addresses in IPv6 are commonly shortened, as many of the 128-bits in the address are set to 0.
For instance, google.com has the address
\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
\texttt{2607:f8b0:400f:806::2004}). Only 24 bits are set to 1 in this address,
giving censors a possible feature to filter on: addresses that have too much
entropy (or even simply bits set) could be suspicious as phantom hosts. To demonstrate and quantify
this problem, we measured 30 minutes of IPv6 traffic to our ISP's /32 network prefix.
Figure~\ref{fig:ipbits} shows a histogram of bits set in the addresses we observed, which are
notably skewed to less than expected if addresses were randomly generated. However, there
are still a significant number of networks that appear to have random-looking addresses,
making it difficult for censors to block these addresses outright. For a specific deployment,
operators should be careful to observe the distribution of addresses in the subnets they use,
and possibly limit to randomizing ``realistic'' bits (e.g. the middle and/or last 32 bits).

@@

\paragraph{Client-side applications}
On the application side, \scheme provides an interesting opportunity to explore
\emph{client mimicking} phantom hosts. Rather than pretend to be a server (e.g.
mask site), our application could connect back to a client after registration
from the phantom host address. Protocols like WebRTC mentioned in
Section~\ref{sec:webrtc} or other peer-to-peer protocols such as BitTorrent,
Skype, or Bitcoin.
